Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-20 paper.tex
Blah

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\title{Spec2Fab: A  Graph-Based Reduction for Fabricating Fabrication Algorithms}

@@

\section{Related Work} 
Here we will review previous algorithms for solving the optimal material assignment problem . We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties. Finally we will briefly review work done on modular shader languages as they have influenced our current work.
\subsection{Material Assignment for Desired Optical Properties}

@@

\subsection{Material Assignment for Desired Mechanical Properties}
Fabricating objects with desire deformation characteristics has been explored less in the literature. Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a desired shape while inflated ~\cite{sko:2012}. Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.
\subsection{Similarities between Methods}
\autoref{tb:algorithms} shows the coordinate reduction method as well as the optimization scheme used in all cited works. A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but rely on a small set of common components to achieve their goals. Thus one could hope to find a small set of components that can be tied together to synthesize existing and new methods. Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}. Our goal in this paper is to produce an analogous mechanism for material assignment problems. 

@@

~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & ??? \\

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}

@@

\section{Related Work} 
Here we will review previous algorithms for solving the optimal material assignment problem . We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties. Finally we will briefly review work done on modular shader languages as they have influenced our current work.

@@

Fabricating objects with desired deformation characteristics has been explored less in the literature. Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a desired shape while inflated ~\cite{sko:2012}. Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.

\autoref{tb:algorithms} shows the coordinate reduction method as well as the optimization scheme used in all cited works. A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components. These, in conjunction with (often off-the-shelf) optimization techniques form new material assignment algorithms. This suggests that one could find a small set of components that can be tied together to synthesize existing and new methods. Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}. Our goal in this paper is to produce an analogous mechanism for material assignment problems. 

@@

~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & SPSA \\
